Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-08-05 manuscript.tex
201600805

\documentclass[Journal,letterpaper]{ascelike-new}
%% Please choose the appropriate document class option:
% "Journal" produces double-spaced manuscripts for ASCE journals.
% "NewProceedings" produces single-spaced manuscripts for ASCE conference proceedings.
% "Proceedings" produces older-style single-spaced manuscripts for ASCE conference proceedings.
%
%% For more details and options, please see the notes in the ascelike-new.cls file.

% Some useful packages...
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
%\usepackage[figurename=Fig.,labelfont=bf,labelsep=period]{caption}
\usepackage{subcaption}
%\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
%\usepackage{newtxtext,newtxmath}
\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
%

\usepackage{tipa}
\usepackage{amsmath}%math
\usepackage{amsthm}%proof
\usepackage{xcolor}%color
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
%\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black]{hyperref}
\usepackage{amsfonts,amssymb}
\usepackage{color,soul}
\usepackage{ulem}
\theoremstyle{plain}
\newtheorem{myas}{Assumption}
\newtheorem{mydef}{Definition}
\newtheorem{mylem}{Lemma}
\newtheorem{mythm}{Theorem}
\newtheorem{mypro}{Properties}
%\theoremstyle{remark}
\theoremstyle{remark}
\newtheorem{myrem}{Remark}

% Please add the first author's last name here for the footer:
\NameTag{AuthorOneLastName, \today}
% Note that this is not displayed if the NoPageNumbers option is used
% in the documentclass declaration.
%
\begin{document}

% You will need to make the title all-caps
\title{Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System}

\author[2]{Zhiqiang Ma}
\author[1]{Guanghui Sun}
\author[2]{Zhengkai Li}

\affil[1]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email. Email: guanghuisun@hit.edu.cn}
\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email.}
%\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}
%\affil[2]{Third affiliation address}

\maketitle

% Please include an abstract:
\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. The tethered satellite system is modelled based on Lagrangian mechanics theory, and to overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal. The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain, and the stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation to guarantee that the asymptotically stability of the deployment dynamics. The numerical simulations are reported to verify the effectiveness of the proposed control laws.
\end{abstract}

\section{Introduction}
The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique makes it possible to develop various applications for space exploration and scientific research, such as space debris removal~\cite{zhao2014thrust}, space elevator~\cite{kojima2015mission}, satellite de-orbit~\cite{zhong2013dynamics,zhong2013long} and the tethered space robot~\cite{huang2014optimal}. Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line}.\par

@@

owing to the boundedness of the expression above, a large enough $\delta$ can be selected such that $\dot V \le 0$. According to the description of Barbalat’s lemmas, it implies that $S_{r2}$ asymptotically converges to zero with the set of suitable designer parameters.\par

@@

%
% Here's the list of references:
%
% \label{section:references}
%\bibliography{ascexmpl-new}

@@

%

>>>>

%\documentclass[draftclsnofoot,onecolumn]{IEEEtran}
\documentclass[3p]{elsarticle}
\usepackage{tipa}
\usepackage{amsmath}%math
\usepackage{amsthm}%proof
\usepackage{xcolor}%color
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black]{hyperref}
\usepackage{amsfonts,amssymb}
\usepackage{color,soul}
\theoremstyle{plain}
\newtheorem{myas}{Assumption}
\newtheorem{mydef}{Definition}
\newtheorem{mylem}{Lemma}
\newtheorem{mythm}{Theorem}
\newtheorem{mypro}{Properties}
%\theoremstyle{remark}
\theoremstyle{remark}
\newtheorem{myrem}{Remark}
\begin{document}
\begin{frontmatter}
\title{Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System}
\author{Zhiqiang Ma}
\author{Guanghui Sun\corref{cor1}}
{\author{Zhengkai Li\corref{cor2}}}
\ead{guanghuisun@hit.edu.cn}
\cortext[cor1]{Corresponding author}
\address{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. The tethered satellite system is modelled based on Lagrangian mechanics theory, and to overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal. The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain, and the stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation to guarantee that the asymptotically stability of the deployment dynamics. The numerical simulations are reported to verify the effectiveness of the proposed control laws.
\end{abstract}
\begin{keyword}
Tethered satellite;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique supports various applications for space exploration and scientific research, such as space debris removal~\cite{zhao2014thrust}, space elevator~\cite{kojima2015mission}, satellite de-orbit~\cite{zhong2013dynamics,zhong2013long} and the tethered space robot~\cite{huang2014optimal}. Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line}.\par

@@

owing to the boundedness of the expression above, a large enough $\delta$ can be selected such that $\dot V \le 0$. According to the description of Barbalat¡¯s lemmas, it implies that $S_{r2}$ asymptotically converges to zero with the set of suitable designer parameters.\par

@@

\section{References}

@@

\bibliographystyle{elsarticle-num}
